Supplementary Information

### 2020-10-07 writing/transect_supplement.Rmd
edits to respond to reviewer comments.  All addressed except supplementary figures.  diff latex is not rendering.

(ref:qual-check) **(a)** per-base error rate; **(b)** expected number of errors per read. Statistics are based on quality scores assigned by technology-specific basecallers. **THIS NEEDS TO BE MENTIONED IN THE TEXT (addresses reviewer comment)**

>>>>

(ref:qual-check) **(a)** per-base error rate; **(b)** expected number of errors per read, with threshold of 3 expected errors marked as a dashed vertical line. Statistics are based on quality scores assigned by technology-specific basecallers.
